---
title: "helianthus_V4_sequence_processing"
author: "Aaron Onufrak"
date: "2023-07-03"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Code Summary

The following code is used to process the *Helianthus 16S* data. Data received by novogene was oddly split so that a single sample was split into multiple forward and reverse files. Prior to the start of this code, data was concatenated by sample ID and read direction. Scripts for that are located in **/Volumes/non_dissertation_projects/odoi_projects/bacteria_v4_data**. The following steps are performed in this code:

1. Remove ambiguous bases
2. Remove adapters and primers
3. Quality filter reads

```{r, warning=FALSE, message=FALSE}
library(dada2)
library(Biostrings)
library(ShortRead)
library(reticulate)
```

# Step 1: Data import and initial quality assessment

```{r,message=FALSE, warning=FALSE}
# Path to all original sequence files
helianthus_bac_path<-"/Volumes/non_dissertation_projects/odoi_projects/bacteria_v4_data/analyses_v4/raw_data_concat"

# Then create objects for the forward and reverse reads
forward_reads_bac_helianthus<-sort(list.files(helianthus_bac_path, pattern=".r1.fq.gz|P[0-9].b.raw_1.fq.gz|Negative_b.raw_1.fq.gz",full.names=TRUE))

reverse_reads_bac_helianthus<-sort(list.files(helianthus_bac_path, pattern=".r2.fq.gz|P[0-9].b.raw_2.fq.gz|Negative_b.raw_2.fq.gz",full.names=TRUE))

# Check number of forward and reverse files. Should be an equal number of forward and reverse files. 
length(forward_reads_bac_helianthus)
length(reverse_reads_bac_helianthus)

# Generate quality plots to assess read quality
forward_qual_profile_raw<-plotQualityProfile(forward_reads_bac_helianthus,aggregate=TRUE)
forward_qual_profile_raw
reverse_qual_profile_raw<-plotQualityProfile(reverse_reads_bac_helianthus,aggregate=TRUE)
reverse_qual_profile_raw

# First we create an object  that strips away the pathway information leaving behind only the filename. We do this using the basename function. 
sample_basename_bac_helianthus<-basename(forward_reads_bac_helianthus)

# We then create an object that contains only our sample names.
samplenames_bac_helianthus<-sub(".r1.*","",sample_basename_bac_helianthus)
samplenames_bac_helianthus<-sub("_b.raw_1.fq.gz.*","",samplenames_bac_helianthus)

# Next we create two path objects that we will store the paths for our filtered forward and reverse reads. 
filtN_forward_reads_bac_helianthus<-file.path(helianthus_bac_path,"all_files_processed","filtN_all_files_processed",paste0("filtN_",basename(forward_reads_bac_helianthus)))
filtN_reverse_reads_bac_helianthus<-file.path(helianthus_bac_path,"all_files_processed","filtN_all_files_processed",paste0("filtN_",basename(reverse_reads_bac_helianthus)))

# We then filter our forward and reverse reads using the filterAndTrim function. Specifying maxN=0 will indicate that sequences with at least 1 ambiguous base will be removed from the dataset. 
filterAndTrim(forward_reads_bac_helianthus,filtN_forward_reads_bac_helianthus,reverse_reads_bac_helianthus,filtN_reverse_reads_bac_helianthus,maxN=0)

forward_qual_profile_filtn<-plotQualityProfile(filtN_forward_reads_bac_helianthus,aggregate=TRUE)
forward_qual_profile_filtn
reverse_qual_profile_filtn<-plotQualityProfile(filtN_reverse_reads_bac_helianthus,aggregate=TRUE)
reverse_qual_profile_filtn


```

# Step 2: Poly-G Trimming, barcode trimming, and primer trimming

```{r}
# Using the system2 function to pass commands to the shell so that we can run fastp from R. In this case, we call cutadapt and pass the argument --version to find out what version of cutadapt we are using. 
library(reticulate)
system2("conda",args=c("run","-n","fastp","fastp --version"),stdout="")

# Create a directory to store the forward and reverse reads after they have been trimmed.
path_polycut_bac_helianthus<-file.path(helianthus_bac_path,"all_files_processed","poly_cutadapt_all_files_processed")
if(!dir.exists(path_polycut_bac_helianthus)) dir.create(path_polycut_bac_helianthus)

polycut_forward_reads_bac_helianthus<-file.path(path_polycut_bac_helianthus,paste0("polycut_",basename(forward_reads_bac_helianthus)))

polycut_reverse_reads_bac_helianthus<-file.path(path_polycut_bac_helianthus,paste0("polycut_",basename(reverse_reads_bac_helianthus)))

for (i in seq_along(forward_reads_bac_helianthus)){
  system2("conda",args=c("run","-n","fastp","fastp",
"-g","-A","-Q","-L",
"-o",polycut_forward_reads_bac_helianthus[i], "-O",polycut_reverse_reads_bac_helianthus[i],
"-i", filtN_forward_reads_bac_helianthus[i],"-I", filtN_reverse_reads_bac_helianthus[i]))
}


# Creating objects that contain the forward and reverse primers used in the study.
fwdbc_1<-"AACGTGAT"
fwdbc_2<-"AAACATCG"
fwdbc_3<-"ATGCCTAA"
fwdbc_4<-"AGTGGTCA"


revbc_1<-"CCGAAGTA"
revbc_2<-"ACCACTGT"
revbc_3<-"ACATTGGC"
revbc_4<-"CATCAAGT"
revbc_5<-"CGCTGATC"
revbc_6<-"ACAAGCTA"
revbc_7<-"CTGTAGCC"
revbc_8<-"AGTACAAG"
revbc_9<-"AACAACCA"
revbc_10<-"AACCGAGA"

revbc_11<-"AACGCTTA"
revbc_12<-"AAGACGGA"
revbc_13<-"ACACAGAA"
revbc_14<-"ACAGCAGA"
revbc_15<-"ACCTCCAA"
revbc_16<-"ACGCTCGA"
revbc_17<-"ACGTATCA"
revbc_18<-"ACTATGCA"
revbc_19<-"AGAGTCAA"
revbc_20<-"AGATCGCA"

revbc_21<-"AGCAGGAA"
revbc_22<-"AGTCACTA"
revbc_23<-"ATCCTGTA"
revbc_24<-"ATTGAGGA"
revbc_25<-"CAACCACA"
revbc_26<-"CAATGGAA"
revbc_27<-"CACTTCGA"
revbc_28<-"CAGCGTTA"
revbc_29<-"CATACCAA"
revbc_30<-"CCAGTTCA"

allorientations<-function(primer){       
  require(Biostrings)     
  dna<-DNAString(primer)                                                    
  orientations<-c(Forward=dna, Complement=Biostrings::complement(dna),Reverse=Biostrings::reverse(dna), 
             RevComp=Biostrings::reverseComplement(dna)) 
  return(sapply(orientations,toString))
}

# Storing all possible orientations of our primers in objects for each primer.
fwdbc_1.ori<-allorientations(fwdbc_1)
fwdbc_2.ori<-allorientations(fwdbc_2)
fwdbc_3.ori<-allorientations(fwdbc_3)
fwdbc_4.ori<-allorientations(fwdbc_4)

revbc_1.ori<-allorientations(revbc_1)
revbc_2.ori<-allorientations(revbc_2)
revbc_3.ori<-allorientations(revbc_3)
revbc_4.ori<-allorientations(revbc_4)
revbc_5.ori<-allorientations(revbc_5)
revbc_6.ori<-allorientations(revbc_6)
revbc_7.ori<-allorientations(revbc_7)
revbc_8.ori<-allorientations(revbc_8)
revbc_9.ori<-allorientations(revbc_9)
revbc_10.ori<-allorientations(revbc_10)

revbc_11.ori<-allorientations(revbc_11)
revbc_12.ori<-allorientations(revbc_12)
revbc_13.ori<-allorientations(revbc_13)
revbc_14.ori<-allorientations(revbc_14)
revbc_15.ori<-allorientations(revbc_15)
revbc_16.ori<-allorientations(revbc_16)
revbc_17.ori<-allorientations(revbc_17)
revbc_18.ori<-allorientations(revbc_18)
revbc_19.ori<-allorientations(revbc_19)
revbc_20.ori<-allorientations(revbc_20)


revbc_21.ori<-allorientations(revbc_21)
revbc_22.ori<-allorientations(revbc_22)
revbc_23.ori<-allorientations(revbc_23)
revbc_24.ori<-allorientations(revbc_24)
revbc_25.ori<-allorientations(revbc_25)
revbc_26.ori<-allorientations(revbc_26)
revbc_27.ori<-allorientations(revbc_27)
revbc_28.ori<-allorientations(revbc_28)
revbc_29.ori<-allorientations(revbc_29)
revbc_30.ori<-allorientations(revbc_30)


# Creating a directory to store the forward and reverse reads after they have been trimmed.
# Create a directory to store the forward and reverse reads after they have been trimmed.
path_bccut_bac_helianthus<-file.path(helianthus_bac_path,"all_files_processed","bc_cutadapt_all_files_processed")
if(!dir.exists(path_bccut_bac_helianthus)) dir.create(path_bccut_bac_helianthus)

bccut_forward_reads_bac_helianthus<-file.path(path_bccut_bac_helianthus,paste0("bccut_",basename(forward_reads_bac_helianthus)))

bccut_reverse_reads_bac_helianthus<-file.path(path_bccut_bac_helianthus,paste0("bccut_",basename(reverse_reads_bac_helianthus)))

# Creating objects containing the forward and reverse primer reverse compliment strings. By using the :: syntax we are able to call a function stored in the dada2 package without having to load the whole dada2 package. In this case we will call the rc function of the dada2 package. The rc function takes a sequence object provided by the user and creates the reverse compliment of the sequence. 
fwdbc_1.rc1<-dada2::rc(fwdbc_1)
fwdbc_2.rc1<-dada2::rc(fwdbc_2)
fwdbc_3.rc1<-dada2::rc(fwdbc_3)
fwdbc_4.rc1<-dada2::rc(fwdbc_4)

revbc_1.rc1<-dada2::rc(revbc_1)
revbc_2.rc1<-dada2::rc(revbc_2)
revbc_3.rc1<-dada2::rc(revbc_3)
revbc_4.rc1<-dada2::rc(revbc_4)
revbc_5.rc1<-dada2::rc(revbc_5)
revbc_6.rc1<-dada2::rc(revbc_6)
revbc_7.rc1<-dada2::rc(revbc_7)
revbc_8.rc1<-dada2::rc(revbc_8)
revbc_9.rc1<-dada2::rc(revbc_9)
revbc_10.rc1<-dada2::rc(revbc_10)

revbc_11.rc1<-dada2::rc(revbc_11)
revbc_12.rc1<-dada2::rc(revbc_12)
revbc_13.rc1<-dada2::rc(revbc_13)
revbc_14.rc1<-dada2::rc(revbc_14)
revbc_15.rc1<-dada2::rc(revbc_15)
revbc_16.rc1<-dada2::rc(revbc_16)
revbc_17.rc1<-dada2::rc(revbc_17)
revbc_18.rc1<-dada2::rc(revbc_18)
revbc_19.rc1<-dada2::rc(revbc_19)
revbc_20.rc1<-dada2::rc(revbc_20)

revbc_21.rc1<-dada2::rc(revbc_21)
revbc_22.rc1<-dada2::rc(revbc_22)
revbc_23.rc1<-dada2::rc(revbc_23)
revbc_24.rc1<-dada2::rc(revbc_24)
revbc_25.rc1<-dada2::rc(revbc_25)
revbc_26.rc1<-dada2::rc(revbc_26)
revbc_27.rc1<-dada2::rc(revbc_27)
revbc_28.rc1<-dada2::rc(revbc_28)
revbc_29.rc1<-dada2::rc(revbc_29)
revbc_30.rc1<-dada2::rc(revbc_30)


# Using the paste function we then create objects that contain the flags for the potential combinations of each forward and reverse primer and the reverse compliment. These flags will serve as the argumentst that we provide to cutadapt. The ^ at the beginning of the sequence indicates that the primer should be removed from the beginning of the sequence. 
fwdbc_1.rev_bc1.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_1.rc1, sep='') 
fwdbc_1.rev_bc2.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_2.rc1, sep='')
fwdbc_1.rev_bc3.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_3.rc1, sep='') 
fwdbc_1.rev_bc4.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_4.rc1, sep='') 
fwdbc_1.rev_bc5.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_5.rc1, sep='') 
fwdbc_1.rev_bc6.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_6.rc1, sep='') 
fwdbc_1.rev_bc7.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_7.rc1, sep='') 
fwdbc_1.rev_bc8.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_8.rc1, sep='') 
fwdbc_1.rev_bc9.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_9.rc1, sep='') 
fwdbc_1.rev_bc10.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_10.rc1, sep='')

fwdbc_1.rev_bc11.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_11.rc1, sep='') 
fwdbc_1.rev_bc12.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_12.rc1, sep='')
fwdbc_1.rev_bc13.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_13.rc1, sep='') 
fwdbc_1.rev_bc14.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_14.rc1, sep='') 
fwdbc_1.rev_bc15.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_15.rc1, sep='') 
fwdbc_1.rev_bc16.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_16.rc1, sep='') 
fwdbc_1.rev_bc17.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_17.rc1, sep='') 
fwdbc_1.rev_bc18.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_18.rc1, sep='') 
fwdbc_1.rev_bc19.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_19.rc1, sep='') 
fwdbc_1.rev_bc20.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_20.rc1, sep='')

fwdbc_1.rev_bc21.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_21.rc1, sep='') 
fwdbc_1.rev_bc22.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_22.rc1, sep='')
fwdbc_1.rev_bc23.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_23.rc1, sep='') 
fwdbc_1.rev_bc24.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_24.rc1, sep='') 
fwdbc_1.rev_bc25.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_25.rc1, sep='') 
fwdbc_1.rev_bc26.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_26.rc1, sep='') 
fwdbc_1.rev_bc27.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_27.rc1, sep='') 
fwdbc_1.rev_bc28.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_28.rc1, sep='') 
fwdbc_1.rev_bc29.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_29.rc1, sep='') 
fwdbc_1.rev_bc30.r1.flags<-paste("-a"," ", "^", fwdbc_1,"...",revbc_30.rc1, sep='')


fwdbc_2.rev_bc1.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_1.rc1, sep='') 
fwdbc_2.rev_bc2.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_2.rc1, sep='')
fwdbc_2.rev_bc3.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_3.rc1, sep='') 
fwdbc_2.rev_bc4.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_4.rc1, sep='') 
fwdbc_2.rev_bc5.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_5.rc1, sep='') 
fwdbc_2.rev_bc6.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_6.rc1, sep='') 
fwdbc_2.rev_bc7.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_7.rc1, sep='') 
fwdbc_2.rev_bc8.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_8.rc1, sep='') 
fwdbc_2.rev_bc9.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_9.rc1, sep='') 
fwdbc_2.rev_bc10.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_10.rc1, sep='')

fwdbc_2.rev_bc11.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_11.rc1, sep='') 
fwdbc_2.rev_bc12.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_12.rc1, sep='')
fwdbc_2.rev_bc13.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_13.rc1, sep='') 
fwdbc_2.rev_bc14.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_14.rc1, sep='') 
fwdbc_2.rev_bc15.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_15.rc1, sep='') 
fwdbc_2.rev_bc16.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_16.rc1, sep='') 
fwdbc_2.rev_bc17.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_17.rc1, sep='') 
fwdbc_2.rev_bc18.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_18.rc1, sep='') 
fwdbc_2.rev_bc19.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_19.rc1, sep='') 
fwdbc_2.rev_bc20.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_20.rc1, sep='')

fwdbc_2.rev_bc21.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_21.rc1, sep='') 
fwdbc_2.rev_bc22.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_22.rc1, sep='')
fwdbc_2.rev_bc23.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_23.rc1, sep='') 
fwdbc_2.rev_bc24.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_24.rc1, sep='') 
fwdbc_2.rev_bc25.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_25.rc1, sep='') 
fwdbc_2.rev_bc26.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_26.rc1, sep='') 
fwdbc_2.rev_bc27.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_27.rc1, sep='') 
fwdbc_2.rev_bc28.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_28.rc1, sep='') 
fwdbc_2.rev_bc29.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_29.rc1, sep='') 
fwdbc_2.rev_bc30.r1.flags<-paste("-a"," ", "^", fwdbc_2,"...",revbc_30.rc1, sep='')

fwdbc_3.rev_bc1.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_1.rc1, sep='') 
fwdbc_3.rev_bc2.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_2.rc1, sep='')
fwdbc_3.rev_bc3.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_3.rc1, sep='') 
fwdbc_3.rev_bc4.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_4.rc1, sep='') 
fwdbc_3.rev_bc5.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_5.rc1, sep='') 
fwdbc_3.rev_bc6.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_6.rc1, sep='') 
fwdbc_3.rev_bc7.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_7.rc1, sep='') 
fwdbc_3.rev_bc8.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_8.rc1, sep='') 
fwdbc_3.rev_bc9.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_9.rc1, sep='') 
fwdbc_3.rev_bc10.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_10.rc1, sep='')

fwdbc_3.rev_bc11.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_11.rc1, sep='') 
fwdbc_3.rev_bc12.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_12.rc1, sep='')
fwdbc_3.rev_bc13.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_13.rc1, sep='') 
fwdbc_3.rev_bc14.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_14.rc1, sep='') 
fwdbc_3.rev_bc15.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_15.rc1, sep='') 
fwdbc_3.rev_bc16.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_16.rc1, sep='') 
fwdbc_3.rev_bc17.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_17.rc1, sep='') 
fwdbc_3.rev_bc18.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_18.rc1, sep='') 
fwdbc_3.rev_bc19.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_19.rc1, sep='') 
fwdbc_3.rev_bc20.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_20.rc1, sep='')

fwdbc_3.rev_bc21.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_21.rc1, sep='') 
fwdbc_3.rev_bc22.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_22.rc1, sep='')
fwdbc_3.rev_bc23.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_23.rc1, sep='') 
fwdbc_3.rev_bc24.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_24.rc1, sep='') 
fwdbc_3.rev_bc25.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_25.rc1, sep='') 
fwdbc_3.rev_bc26.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_26.rc1, sep='') 
fwdbc_3.rev_bc27.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_27.rc1, sep='') 
fwdbc_3.rev_bc28.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_28.rc1, sep='') 
fwdbc_3.rev_bc29.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_29.rc1, sep='') 
fwdbc_3.rev_bc30.r1.flags<-paste("-a"," ", "^", fwdbc_3,"...",revbc_30.rc1, sep='')

fwdbc_4.rev_bc1.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_1.rc1, sep='') 
fwdbc_4.rev_bc2.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_2.rc1, sep='')
fwdbc_4.rev_bc3.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_3.rc1, sep='') 
fwdbc_4.rev_bc4.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_4.rc1, sep='') 
fwdbc_4.rev_bc5.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_5.rc1, sep='') 
fwdbc_4.rev_bc6.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_6.rc1, sep='') 
fwdbc_4.rev_bc7.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_7.rc1, sep='') 
fwdbc_4.rev_bc8.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_8.rc1, sep='') 
fwdbc_4.rev_bc9.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_9.rc1, sep='') 
fwdbc_4.rev_bc10.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_10.rc1, sep='')

fwdbc_4.rev_bc11.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_11.rc1, sep='') 
fwdbc_4.rev_bc12.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_12.rc1, sep='')
fwdbc_4.rev_bc13.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_13.rc1, sep='') 
fwdbc_4.rev_bc14.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_14.rc1, sep='') 
fwdbc_4.rev_bc15.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_15.rc1, sep='') 
fwdbc_4.rev_bc16.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_16.rc1, sep='') 
fwdbc_4.rev_bc17.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_17.rc1, sep='') 
fwdbc_4.rev_bc18.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_18.rc1, sep='') 
fwdbc_4.rev_bc19.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_19.rc1, sep='') 
fwdbc_4.rev_bc20.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_20.rc1, sep='')

fwdbc_4.rev_bc21.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_21.rc1, sep='') 
fwdbc_4.rev_bc22.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_22.rc1, sep='')
fwdbc_4.rev_bc23.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_23.rc1, sep='') 
fwdbc_4.rev_bc24.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_24.rc1, sep='') 
fwdbc_4.rev_bc25.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_25.rc1, sep='') 
fwdbc_4.rev_bc26.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_26.rc1, sep='') 
fwdbc_4.rev_bc27.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_27.rc1, sep='') 
fwdbc_4.rev_bc28.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_28.rc1, sep='') 
fwdbc_4.rev_bc29.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_29.rc1, sep='') 
fwdbc_4.rev_bc30.r1.flags<-paste("-a"," ", "^", fwdbc_4,"...",revbc_30.rc1, sep='')

revbc_1.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_1,"...",fwdbc_1.rc1, sep='') 
revbc_1.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_1,"...",fwdbc_2.rc1, sep='') 
revbc_1.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_1,"...",fwdbc_3.rc1, sep='') 
revbc_1.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_1,"...",fwdbc_4.rc1, sep='') 

revbc_2.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_2,"...",fwdbc_1.rc1, sep='') 
revbc_2.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_2,"...",fwdbc_2.rc1, sep='') 
revbc_2.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_2,"...",fwdbc_3.rc1, sep='') 
revbc_2.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_2,"...",fwdbc_4.rc1, sep='') 

revbc_3.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_3,"...",fwdbc_1.rc1, sep='') 
revbc_3.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_3,"...",fwdbc_2.rc1, sep='') 
revbc_3.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_3,"...",fwdbc_3.rc1, sep='') 
revbc_3.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_3,"...",fwdbc_4.rc1, sep='') 

revbc_4.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_4,"...",fwdbc_1.rc1, sep='') 
revbc_4.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_4,"...",fwdbc_2.rc1, sep='') 
revbc_4.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_4,"...",fwdbc_3.rc1, sep='') 
revbc_4.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_4,"...",fwdbc_4.rc1, sep='') 

revbc_5.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_5,"...",fwdbc_1.rc1, sep='') 
revbc_5.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_5,"...",fwdbc_2.rc1, sep='') 
revbc_5.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_5,"...",fwdbc_3.rc1, sep='') 
revbc_5.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_5,"...",fwdbc_4.rc1, sep='') 

revbc_6.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_6,"...",fwdbc_1.rc1, sep='') 
revbc_6.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_6,"...",fwdbc_2.rc1, sep='') 
revbc_6.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_6,"...",fwdbc_3.rc1, sep='') 
revbc_6.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_6,"...",fwdbc_4.rc1, sep='') 

revbc_7.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_7,"...",fwdbc_1.rc1, sep='') 
revbc_7.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_7,"...",fwdbc_2.rc1, sep='') 
revbc_7.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_7,"...",fwdbc_3.rc1, sep='') 
revbc_7.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_7,"...",fwdbc_4.rc1, sep='') 

revbc_8.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_8,"...",fwdbc_1.rc1, sep='') 
revbc_8.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_8,"...",fwdbc_2.rc1, sep='') 
revbc_8.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_8,"...",fwdbc_3.rc1, sep='') 
revbc_8.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_8,"...",fwdbc_4.rc1, sep='') 

revbc_9.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_9,"...",fwdbc_1.rc1, sep='') 
revbc_9.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_9,"...",fwdbc_2.rc1, sep='') 
revbc_9.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_9,"...",fwdbc_3.rc1, sep='') 
revbc_9.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_9,"...",fwdbc_4.rc1, sep='') 


revbc_10.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_10,"...",fwdbc_1.rc1, sep='') 
revbc_10.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_10,"...",fwdbc_2.rc1, sep='') 
revbc_10.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_10,"...",fwdbc_3.rc1, sep='') 
revbc_10.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_10,"...",fwdbc_4.rc1, sep='') 



revbc_11.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_11,"...",fwdbc_1.rc1, sep='') 
revbc_11.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_11,"...",fwdbc_2.rc1, sep='') 
revbc_11.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_11,"...",fwdbc_3.rc1, sep='') 
revbc_11.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_11,"...",fwdbc_4.rc1, sep='') 

revbc_12.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_12,"...",fwdbc_1.rc1, sep='') 
revbc_12.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_12,"...",fwdbc_2.rc1, sep='') 
revbc_12.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_12,"...",fwdbc_3.rc1, sep='') 
revbc_12.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_12,"...",fwdbc_4.rc1, sep='') 

revbc_13.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_13,"...",fwdbc_1.rc1, sep='') 
revbc_13.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_13,"...",fwdbc_2.rc1, sep='') 
revbc_13.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_13,"...",fwdbc_3.rc1, sep='') 
revbc_13.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_13,"...",fwdbc_4.rc1, sep='') 

revbc_14.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_14,"...",fwdbc_1.rc1, sep='') 
revbc_14.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_14,"...",fwdbc_2.rc1, sep='') 
revbc_14.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_14,"...",fwdbc_3.rc1, sep='') 
revbc_14.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_14,"...",fwdbc_4.rc1, sep='') 

revbc_15.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_15,"...",fwdbc_1.rc1, sep='') 
revbc_15.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_15,"...",fwdbc_2.rc1, sep='') 
revbc_15.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_15,"...",fwdbc_3.rc1, sep='') 
revbc_15.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_15,"...",fwdbc_4.rc1, sep='') 

revbc_16.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_16,"...",fwdbc_1.rc1, sep='') 
revbc_16.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_16,"...",fwdbc_2.rc1, sep='') 
revbc_16.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_16,"...",fwdbc_3.rc1, sep='') 
revbc_16.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_16,"...",fwdbc_4.rc1, sep='') 

revbc_17.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_17,"...",fwdbc_1.rc1, sep='') 
revbc_17.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_17,"...",fwdbc_2.rc1, sep='') 
revbc_17.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_17,"...",fwdbc_3.rc1, sep='') 
revbc_17.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_17,"...",fwdbc_4.rc1, sep='') 

revbc_18.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_18,"...",fwdbc_1.rc1, sep='') 
revbc_18.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_18,"...",fwdbc_2.rc1, sep='') 
revbc_18.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_18,"...",fwdbc_3.rc1, sep='') 
revbc_18.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_18,"...",fwdbc_4.rc1, sep='') 

revbc_19.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_19,"...",fwdbc_1.rc1, sep='') 
revbc_19.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_19,"...",fwdbc_2.rc1, sep='') 
revbc_19.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_19,"...",fwdbc_3.rc1, sep='') 
revbc_19.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_19,"...",fwdbc_4.rc1, sep='') 

revbc_20.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_20,"...",fwdbc_1.rc1, sep='') 
revbc_20.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_20,"...",fwdbc_2.rc1, sep='') 
revbc_20.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_20,"...",fwdbc_3.rc1, sep='') 
revbc_20.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_20,"...",fwdbc_4.rc1, sep='') 

revbc_21.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_21,"...",fwdbc_1.rc1, sep='') 
revbc_21.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_21,"...",fwdbc_2.rc1, sep='') 
revbc_21.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_21,"...",fwdbc_3.rc1, sep='') 
revbc_21.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_21,"...",fwdbc_4.rc1, sep='') 

revbc_22.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_22,"...",fwdbc_1.rc1, sep='') 
revbc_22.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_22,"...",fwdbc_2.rc1, sep='') 
revbc_22.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_22,"...",fwdbc_3.rc1, sep='') 
revbc_22.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_22,"...",fwdbc_4.rc1, sep='') 

revbc_23.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_23,"...",fwdbc_1.rc1, sep='') 
revbc_23.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_23,"...",fwdbc_2.rc1, sep='') 
revbc_23.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_23,"...",fwdbc_3.rc1, sep='') 
revbc_23.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_23,"...",fwdbc_4.rc1, sep='') 

revbc_24.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_24,"...",fwdbc_1.rc1, sep='') 
revbc_24.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_24,"...",fwdbc_2.rc1, sep='') 
revbc_24.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_24,"...",fwdbc_3.rc1, sep='') 
revbc_24.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_24,"...",fwdbc_4.rc1, sep='') 

revbc_25.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_25,"...",fwdbc_1.rc1, sep='') 
revbc_25.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_25,"...",fwdbc_2.rc1, sep='') 
revbc_25.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_25,"...",fwdbc_3.rc1, sep='') 
revbc_25.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_25,"...",fwdbc_4.rc1, sep='') 

revbc_26.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_26,"...",fwdbc_1.rc1, sep='') 
revbc_26.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_26,"...",fwdbc_2.rc1, sep='') 
revbc_26.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_26,"...",fwdbc_3.rc1, sep='') 
revbc_26.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_26,"...",fwdbc_4.rc1, sep='') 

revbc_27.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_27,"...",fwdbc_1.rc1, sep='') 
revbc_27.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_27,"...",fwdbc_2.rc1, sep='') 
revbc_27.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_27,"...",fwdbc_3.rc1, sep='') 
revbc_27.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_27,"...",fwdbc_4.rc1, sep='') 

revbc_28.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_28,"...",fwdbc_1.rc1, sep='') 
revbc_28.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_28,"...",fwdbc_2.rc1, sep='') 
revbc_28.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_28,"...",fwdbc_3.rc1, sep='') 
revbc_28.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_28,"...",fwdbc_4.rc1, sep='') 

revbc_29.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_29,"...",fwdbc_1.rc1, sep='') 
revbc_29.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_29,"...",fwdbc_2.rc1, sep='') 
revbc_29.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_29,"...",fwdbc_3.rc1, sep='') 
revbc_29.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_29,"...",fwdbc_4.rc1, sep='') 

revbc_30.fwdbc_1.r2f.flags<-paste("-a"," ", "^", revbc_30,"...",fwdbc_1.rc1, sep='') 
revbc_30.fwdbc_2.r2f.flags<-paste("-a"," ", "^", revbc_30,"...",fwdbc_2.rc1, sep='') 
revbc_30.fwdbc_3.r2f.flags<-paste("-a"," ", "^", revbc_30,"...",fwdbc_3.rc1, sep='') 
revbc_30.fwdbc_4.r2f.flags<-paste("-a"," ", "^", revbc_30,"...",fwdbc_4.rc1, sep='') 
 
revbc_1.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_1,"...",fwdbc_1.rc1, sep='') 
revbc_1.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_1,"...",fwdbc_2.rc1, sep='') 
revbc_1.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_1,"...",fwdbc_3.rc1, sep='') 
revbc_1.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_1,"...",fwdbc_4.rc1, sep='') 

revbc_2.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_2,"...",fwdbc_1.rc1, sep='') 
revbc_2.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_2,"...",fwdbc_2.rc1, sep='') 
revbc_2.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_2,"...",fwdbc_3.rc1, sep='') 
revbc_2.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_2,"...",fwdbc_4.rc1, sep='') 

revbc_3.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_3,"...",fwdbc_1.rc1, sep='') 
revbc_3.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_3,"...",fwdbc_2.rc1, sep='') 
revbc_3.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_3,"...",fwdbc_3.rc1, sep='') 
revbc_3.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_3,"...",fwdbc_4.rc1, sep='') 

revbc_4.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_4,"...",fwdbc_1.rc1, sep='') 
revbc_4.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_4,"...",fwdbc_2.rc1, sep='') 
revbc_4.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_4,"...",fwdbc_3.rc1, sep='') 
revbc_4.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_4,"...",fwdbc_4.rc1, sep='') 

revbc_5.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_5,"...",fwdbc_1.rc1, sep='') 
revbc_5.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_5,"...",fwdbc_2.rc1, sep='') 
revbc_5.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_5,"...",fwdbc_3.rc1, sep='') 
revbc_5.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_5,"...",fwdbc_4.rc1, sep='') 

revbc_6.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_6,"...",fwdbc_1.rc1, sep='') 
revbc_6.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_6,"...",fwdbc_2.rc1, sep='') 
revbc_6.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_6,"...",fwdbc_3.rc1, sep='') 
revbc_6.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_6,"...",fwdbc_4.rc1, sep='') 

revbc_7.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_7,"...",fwdbc_1.rc1, sep='') 
revbc_7.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_7,"...",fwdbc_2.rc1, sep='') 
revbc_7.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_7,"...",fwdbc_3.rc1, sep='') 
revbc_7.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_7,"...",fwdbc_4.rc1, sep='') 

revbc_8.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_8,"...",fwdbc_1.rc1, sep='') 
revbc_8.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_8,"...",fwdbc_2.rc1, sep='') 
revbc_8.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_8,"...",fwdbc_3.rc1, sep='') 
revbc_8.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_8,"...",fwdbc_4.rc1, sep='') 

revbc_9.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_9,"...",fwdbc_1.rc1, sep='') 
revbc_9.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_9,"...",fwdbc_2.rc1, sep='') 
revbc_9.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_9,"...",fwdbc_3.rc1, sep='') 
revbc_9.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_9,"...",fwdbc_4.rc1, sep='') 

revbc_10.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_10,"...",fwdbc_1.rc1, sep='') 
revbc_10.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_10,"...",fwdbc_2.rc1, sep='') 
revbc_10.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_10,"...",fwdbc_3.rc1, sep='') 
revbc_10.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_10,"...",fwdbc_4.rc1, sep='') 

revbc_11.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_11,"...",fwdbc_1.rc1, sep='') 
revbc_11.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_11,"...",fwdbc_2.rc1, sep='') 
revbc_11.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_11,"...",fwdbc_3.rc1, sep='') 
revbc_11.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_11,"...",fwdbc_4.rc1, sep='') 

revbc_12.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_12,"...",fwdbc_1.rc1, sep='') 
revbc_12.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_12,"...",fwdbc_2.rc1, sep='') 
revbc_12.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_12,"...",fwdbc_3.rc1, sep='') 
revbc_12.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_12,"...",fwdbc_4.rc1, sep='') 

revbc_13.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_13,"...",fwdbc_1.rc1, sep='') 
revbc_13.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_13,"...",fwdbc_2.rc1, sep='') 
revbc_13.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_13,"...",fwdbc_3.rc1, sep='') 
revbc_13.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_13,"...",fwdbc_4.rc1, sep='') 

revbc_14.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_14,"...",fwdbc_1.rc1, sep='') 
revbc_14.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_14,"...",fwdbc_2.rc1, sep='') 
revbc_14.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_14,"...",fwdbc_3.rc1, sep='') 
revbc_14.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_14,"...",fwdbc_4.rc1, sep='') 

revbc_15.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_15,"...",fwdbc_1.rc1, sep='') 
revbc_15.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_15,"...",fwdbc_2.rc1, sep='') 
revbc_15.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_15,"...",fwdbc_3.rc1, sep='') 
revbc_15.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_15,"...",fwdbc_4.rc1, sep='') 


revbc_16.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_16,"...",fwdbc_1.rc1, sep='') 
revbc_16.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_16,"...",fwdbc_2.rc1, sep='') 
revbc_16.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_16,"...",fwdbc_3.rc1, sep='') 
revbc_16.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_16,"...",fwdbc_4.rc1, sep='') 

revbc_17.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_17,"...",fwdbc_1.rc1, sep='') 
revbc_17.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_17,"...",fwdbc_2.rc1, sep='') 
revbc_17.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_17,"...",fwdbc_3.rc1, sep='') 
revbc_17.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_17,"...",fwdbc_4.rc1, sep='') 

revbc_18.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_18,"...",fwdbc_1.rc1, sep='') 
revbc_18.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_18,"...",fwdbc_2.rc1, sep='') 
revbc_18.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_18,"...",fwdbc_3.rc1, sep='') 
revbc_18.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_18,"...",fwdbc_4.rc1, sep='') 

revbc_19.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_19,"...",fwdbc_1.rc1, sep='') 
revbc_19.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_19,"...",fwdbc_2.rc1, sep='') 
revbc_19.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_19,"...",fwdbc_3.rc1, sep='') 
revbc_19.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_19,"...",fwdbc_4.rc1, sep='') 

revbc_20.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_20,"...",fwdbc_1.rc1, sep='') 
revbc_20.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_20,"...",fwdbc_2.rc1, sep='') 
revbc_20.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_20,"...",fwdbc_3.rc1, sep='') 
revbc_20.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_20,"...",fwdbc_4.rc1, sep='') 


revbc_21.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_21,"...",fwdbc_1.rc1, sep='') 
revbc_21.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_21,"...",fwdbc_2.rc1, sep='') 
revbc_21.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_21,"...",fwdbc_3.rc1, sep='') 
revbc_21.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_21,"...",fwdbc_4.rc1, sep='') 

revbc_22.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_22,"...",fwdbc_1.rc1, sep='') 
revbc_22.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_22,"...",fwdbc_2.rc1, sep='') 
revbc_22.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_22,"...",fwdbc_3.rc1, sep='') 
revbc_22.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_22,"...",fwdbc_4.rc1, sep='') 

revbc_23.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_23,"...",fwdbc_1.rc1, sep='') 
revbc_23.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_23,"...",fwdbc_2.rc1, sep='') 
revbc_23.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_23,"...",fwdbc_3.rc1, sep='') 
revbc_23.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_23,"...",fwdbc_4.rc1, sep='') 

revbc_24.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_24,"...",fwdbc_1.rc1, sep='') 
revbc_24.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_24,"...",fwdbc_2.rc1, sep='') 
revbc_24.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_24,"...",fwdbc_3.rc1, sep='') 
revbc_24.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_24,"...",fwdbc_4.rc1, sep='') 

revbc_25.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_25,"...",fwdbc_1.rc1, sep='') 
revbc_25.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_25,"...",fwdbc_2.rc1, sep='') 
revbc_25.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_25,"...",fwdbc_3.rc1, sep='') 
revbc_25.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_25,"...",fwdbc_4.rc1, sep='') 

revbc_26.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_26,"...",fwdbc_1.rc1, sep='') 
revbc_26.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_26,"...",fwdbc_2.rc1, sep='') 
revbc_26.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_26,"...",fwdbc_3.rc1, sep='') 
revbc_26.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_26,"...",fwdbc_4.rc1, sep='') 
 
revbc_27.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_27,"...",fwdbc_1.rc1, sep='') 
revbc_27.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_27,"...",fwdbc_2.rc1, sep='') 
revbc_27.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_27,"...",fwdbc_3.rc1, sep='') 
revbc_27.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_27,"...",fwdbc_4.rc1, sep='') 

revbc_28.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_28,"...",fwdbc_1.rc1, sep='') 
revbc_28.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_28,"...",fwdbc_2.rc1, sep='') 
revbc_28.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_28,"...",fwdbc_3.rc1, sep='') 
revbc_28.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_28,"...",fwdbc_4.rc1, sep='') 

revbc_29.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_29,"...",fwdbc_1.rc1, sep='') 
revbc_29.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_29,"...",fwdbc_2.rc1, sep='') 
revbc_29.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_29,"...",fwdbc_3.rc1, sep='') 
revbc_29.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_29,"...",fwdbc_4.rc1, sep='') 

revbc_30.fwdbc_1.r2.flags<-paste("-A"," ", "^", revbc_30,"...",fwdbc_1.rc1, sep='') 
revbc_30.fwdbc_2.r2.flags<-paste("-A"," ", "^", revbc_30,"...",fwdbc_2.rc1, sep='') 
revbc_30.fwdbc_3.r2.flags<-paste("-A"," ", "^", revbc_30,"...",fwdbc_3.rc1, sep='') 
revbc_30.fwdbc_4.r2.flags<-paste("-A"," ", "^", revbc_30,"...",fwdbc_4.rc1, sep='') 

fwdbc_1.rev_bc1.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_1.rc1, sep='') 
fwdbc_1.rev_bc2.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_2.rc1, sep='')
fwdbc_1.rev_bc3.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_3.rc1, sep='') 
fwdbc_1.rev_bc4.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_4.rc1, sep='') 
fwdbc_1.rev_bc5.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_5.rc1, sep='') 
fwdbc_1.rev_bc6.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_6.rc1, sep='') 
fwdbc_1.rev_bc7.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_7.rc1, sep='') 
fwdbc_1.rev_bc8.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_8.rc1, sep='') 
fwdbc_1.rev_bc9.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_9.rc1, sep='') 
fwdbc_1.rev_bc10.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_10.rc1, sep='')

fwdbc_1.rev_bc11.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_11.rc1, sep='') 
fwdbc_1.rev_bc12.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_12.rc1, sep='')
fwdbc_1.rev_bc13.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_13.rc1, sep='') 
fwdbc_1.rev_bc14.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_14.rc1, sep='') 
fwdbc_1.rev_bc15.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_15.rc1, sep='') 
fwdbc_1.rev_bc16.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_16.rc1, sep='') 
fwdbc_1.rev_bc17.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_17.rc1, sep='') 
fwdbc_1.rev_bc18.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_18.rc1, sep='') 
fwdbc_1.rev_bc19.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_19.rc1, sep='') 
fwdbc_1.rev_bc20.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_20.rc1, sep='')

fwdbc_1.rev_bc21.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_21.rc1, sep='') 
fwdbc_1.rev_bc22.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_22.rc1, sep='')
fwdbc_1.rev_bc23.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_23.rc1, sep='') 
fwdbc_1.rev_bc24.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_24.rc1, sep='') 
fwdbc_1.rev_bc25.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_25.rc1, sep='') 
fwdbc_1.rev_bc26.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_26.rc1, sep='') 
fwdbc_1.rev_bc27.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_27.rc1, sep='') 
fwdbc_1.rev_bc28.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_28.rc1, sep='') 
fwdbc_1.rev_bc29.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_29.rc1, sep='') 
fwdbc_1.rev_bc30.r1r.flags<-paste("-A"," ", "^", fwdbc_1,"...",revbc_30.rc1, sep='')

fwdbc_2.rev_bc1.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_1.rc1, sep='') 
fwdbc_2.rev_bc2.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_2.rc1, sep='')
fwdbc_2.rev_bc3.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_3.rc1, sep='') 
fwdbc_2.rev_bc4.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_4.rc1, sep='') 
fwdbc_2.rev_bc5.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_5.rc1, sep='') 
fwdbc_2.rev_bc6.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_6.rc1, sep='') 
fwdbc_2.rev_bc7.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_7.rc1, sep='') 
fwdbc_2.rev_bc8.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_8.rc1, sep='') 
fwdbc_2.rev_bc9.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_9.rc1, sep='') 
fwdbc_2.rev_bc10.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_10.rc1, sep='')

fwdbc_2.rev_bc11.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_11.rc1, sep='') 
fwdbc_2.rev_bc12.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_12.rc1, sep='')
fwdbc_2.rev_bc13.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_13.rc1, sep='') 
fwdbc_2.rev_bc14.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_14.rc1, sep='') 
fwdbc_2.rev_bc15.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_15.rc1, sep='') 
fwdbc_2.rev_bc16.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_16.rc1, sep='') 
fwdbc_2.rev_bc17.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_17.rc1, sep='') 
fwdbc_2.rev_bc18.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_18.rc1, sep='') 
fwdbc_2.rev_bc19.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_19.rc1, sep='') 
fwdbc_2.rev_bc20.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_20.rc1, sep='')

fwdbc_2.rev_bc21.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_21.rc1, sep='') 
fwdbc_2.rev_bc22.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_22.rc1, sep='')
fwdbc_2.rev_bc23.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_23.rc1, sep='') 
fwdbc_2.rev_bc24.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_24.rc1, sep='') 
fwdbc_2.rev_bc25.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_25.rc1, sep='') 
fwdbc_2.rev_bc26.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_26.rc1, sep='') 
fwdbc_2.rev_bc27.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_27.rc1, sep='') 
fwdbc_2.rev_bc28.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_28.rc1, sep='') 
fwdbc_2.rev_bc29.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_29.rc1, sep='') 
fwdbc_2.rev_bc30.r1r.flags<-paste("-A"," ", "^", fwdbc_2,"...",revbc_30.rc1, sep='')

fwdbc_3.rev_bc1.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_1.rc1, sep='') 
fwdbc_3.rev_bc2.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_2.rc1, sep='')
fwdbc_3.rev_bc3.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_3.rc1, sep='') 
fwdbc_3.rev_bc4.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_4.rc1, sep='') 
fwdbc_3.rev_bc5.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_5.rc1, sep='') 
fwdbc_3.rev_bc6.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_6.rc1, sep='') 
fwdbc_3.rev_bc7.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_7.rc1, sep='') 
fwdbc_3.rev_bc8.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_8.rc1, sep='') 
fwdbc_3.rev_bc9.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_9.rc1, sep='') 
fwdbc_3.rev_bc10.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_10.rc1, sep='')

fwdbc_3.rev_bc11.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_11.rc1, sep='') 
fwdbc_3.rev_bc12.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_12.rc1, sep='')
fwdbc_3.rev_bc13.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_13.rc1, sep='') 
fwdbc_3.rev_bc14.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_14.rc1, sep='') 
fwdbc_3.rev_bc15.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_15.rc1, sep='') 
fwdbc_3.rev_bc16.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_16.rc1, sep='') 
fwdbc_3.rev_bc17.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_17.rc1, sep='') 
fwdbc_3.rev_bc18.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_18.rc1, sep='') 
fwdbc_3.rev_bc19.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_19.rc1, sep='') 
fwdbc_3.rev_bc20.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_20.rc1, sep='')

fwdbc_3.rev_bc21.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_21.rc1, sep='') 
fwdbc_3.rev_bc22.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_22.rc1, sep='')
fwdbc_3.rev_bc23.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_23.rc1, sep='') 
fwdbc_3.rev_bc24.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_24.rc1, sep='') 
fwdbc_3.rev_bc25.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_25.rc1, sep='') 
fwdbc_3.rev_bc26.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_26.rc1, sep='') 
fwdbc_3.rev_bc27.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_27.rc1, sep='') 
fwdbc_3.rev_bc28.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_28.rc1, sep='') 
fwdbc_3.rev_bc29.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_29.rc1, sep='') 
fwdbc_3.rev_bc30.r1r.flags<-paste("-A"," ", "^", fwdbc_3,"...",revbc_30.rc1, sep='')

fwdbc_4.rev_bc1.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_1.rc1, sep='') 
fwdbc_4.rev_bc2.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_2.rc1, sep='')
fwdbc_4.rev_bc3.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_3.rc1, sep='') 
fwdbc_4.rev_bc4.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_4.rc1, sep='') 
fwdbc_4.rev_bc5.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_5.rc1, sep='') 
fwdbc_4.rev_bc6.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_6.rc1, sep='') 
fwdbc_4.rev_bc7.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_7.rc1, sep='') 
fwdbc_4.rev_bc8.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_8.rc1, sep='') 
fwdbc_4.rev_bc9.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_9.rc1, sep='') 
fwdbc_4.rev_bc10.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_10.rc1, sep='')

fwdbc_4.rev_bc11.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_11.rc1, sep='') 
fwdbc_4.rev_bc12.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_12.rc1, sep='')
fwdbc_4.rev_bc13.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_13.rc1, sep='') 
fwdbc_4.rev_bc14.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_14.rc1, sep='') 
fwdbc_4.rev_bc15.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_15.rc1, sep='') 
fwdbc_4.rev_bc16.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_16.rc1, sep='') 
fwdbc_4.rev_bc17.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_17.rc1, sep='') 
fwdbc_4.rev_bc18.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_18.rc1, sep='') 
fwdbc_4.rev_bc19.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_19.rc1, sep='') 
fwdbc_4.rev_bc20.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_20.rc1, sep='')

fwdbc_4.rev_bc21.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_21.rc1, sep='') 
fwdbc_4.rev_bc22.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_22.rc1, sep='')
fwdbc_4.rev_bc23.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_23.rc1, sep='') 
fwdbc_4.rev_bc24.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_24.rc1, sep='') 
fwdbc_4.rev_bc25.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_25.rc1, sep='') 
fwdbc_4.rev_bc26.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_26.rc1, sep='') 
fwdbc_4.rev_bc27.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_27.rc1, sep='') 
fwdbc_4.rev_bc28.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_28.rc1, sep='') 
fwdbc_4.rev_bc29.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_29.rc1, sep='') 
fwdbc_4.rev_bc30.r1r.flags<-paste("-A"," ", "^", fwdbc_4,"...",revbc_30.rc1, sep='')





for (i in seq_along(forward_reads_bac_helianthus)){
  system2("conda",args=c("run","-n","cutadaptenv","cutadapt",
    fwdbc_1.rev_bc1.r1.flags,
fwdbc_1.rev_bc2.r1.flags,
fwdbc_1.rev_bc3.r1.flags,
fwdbc_1.rev_bc4.r1.flags,
fwdbc_1.rev_bc5.r1.flags,
fwdbc_1.rev_bc6.r1.flags,
fwdbc_1.rev_bc7.r1.flags,
fwdbc_1.rev_bc8.r1.flags,
fwdbc_1.rev_bc9.r1.flags,
fwdbc_1.rev_bc10.r1.flags,

fwdbc_1.rev_bc11.r1.flags,
fwdbc_1.rev_bc12.r1.flags,
fwdbc_1.rev_bc13.r1.flags,
fwdbc_1.rev_bc14.r1.flags,
fwdbc_1.rev_bc15.r1.flags,
fwdbc_1.rev_bc16.r1.flags,
fwdbc_1.rev_bc17.r1.flags,
fwdbc_1.rev_bc18.r1.flags,
fwdbc_1.rev_bc19.r1.flags,
fwdbc_1.rev_bc20.r1.flags,

fwdbc_1.rev_bc21.r1.flags,
fwdbc_1.rev_bc22.r1.flags,
fwdbc_1.rev_bc23.r1.flags,
fwdbc_1.rev_bc24.r1.flags,
fwdbc_1.rev_bc25.r1.flags,
fwdbc_1.rev_bc26.r1.flags,
fwdbc_1.rev_bc27.r1.flags,
fwdbc_1.rev_bc28.r1.flags,
fwdbc_1.rev_bc29.r1.flags,
fwdbc_1.rev_bc30.r1.flags,


fwdbc_2.rev_bc1.r1.flags,
fwdbc_2.rev_bc2.r1.flags,
fwdbc_2.rev_bc3.r1.flags,
fwdbc_2.rev_bc4.r1.flags,
fwdbc_2.rev_bc5.r1.flags,
fwdbc_2.rev_bc6.r1.flags,
fwdbc_2.rev_bc7.r1.flags,
fwdbc_2.rev_bc8.r1.flags,
fwdbc_2.rev_bc9.r1.flags,
fwdbc_2.rev_bc10.r1.flags,

fwdbc_2.rev_bc11.r1.flags,
fwdbc_2.rev_bc12.r1.flags,
fwdbc_2.rev_bc13.r1.flags,
fwdbc_2.rev_bc14.r1.flags,
fwdbc_2.rev_bc15.r1.flags,
fwdbc_2.rev_bc16.r1.flags,
fwdbc_2.rev_bc17.r1.flags,
fwdbc_2.rev_bc18.r1.flags,
fwdbc_2.rev_bc19.r1.flags,
fwdbc_2.rev_bc20.r1.flags,

fwdbc_2.rev_bc21.r1.flags,
fwdbc_2.rev_bc22.r1.flags,
fwdbc_2.rev_bc23.r1.flags,
fwdbc_2.rev_bc24.r1.flags,
fwdbc_2.rev_bc25.r1.flags,
fwdbc_2.rev_bc26.r1.flags,
fwdbc_2.rev_bc27.r1.flags,
fwdbc_2.rev_bc28.r1.flags,
fwdbc_2.rev_bc29.r1.flags,
fwdbc_2.rev_bc30.r1.flags,

fwdbc_3.rev_bc1.r1.flags,
fwdbc_3.rev_bc2.r1.flags,
fwdbc_3.rev_bc3.r1.flags,
fwdbc_3.rev_bc4.r1.flags,
fwdbc_3.rev_bc5.r1.flags,
fwdbc_3.rev_bc6.r1.flags,
fwdbc_3.rev_bc7.r1.flags,
fwdbc_3.rev_bc8.r1.flags,
fwdbc_3.rev_bc9.r1.flags,
fwdbc_3.rev_bc10.r1.flags,

fwdbc_3.rev_bc11.r1.flags,
fwdbc_3.rev_bc12.r1.flags,
fwdbc_3.rev_bc13.r1.flags,
fwdbc_3.rev_bc14.r1.flags,
fwdbc_3.rev_bc15.r1.flags,
fwdbc_3.rev_bc16.r1.flags,
fwdbc_3.rev_bc17.r1.flags,
fwdbc_3.rev_bc18.r1.flags,
fwdbc_3.rev_bc19.r1.flags,
fwdbc_3.rev_bc20.r1.flags,

fwdbc_3.rev_bc21.r1.flags,
fwdbc_3.rev_bc22.r1.flags,
fwdbc_3.rev_bc23.r1.flags,
fwdbc_3.rev_bc24.r1.flags,
fwdbc_3.rev_bc25.r1.flags,
fwdbc_3.rev_bc26.r1.flags,
fwdbc_3.rev_bc27.r1.flags,
fwdbc_3.rev_bc28.r1.flags,
fwdbc_3.rev_bc29.r1.flags,
fwdbc_3.rev_bc30.r1.flags,

fwdbc_4.rev_bc1.r1.flags,
fwdbc_4.rev_bc2.r1.flags,
fwdbc_4.rev_bc3.r1.flags,
fwdbc_4.rev_bc4.r1.flags,
fwdbc_4.rev_bc5.r1.flags,
fwdbc_4.rev_bc6.r1.flags,
fwdbc_4.rev_bc7.r1.flags,
fwdbc_4.rev_bc8.r1.flags,
fwdbc_4.rev_bc9.r1.flags,
fwdbc_4.rev_bc10.r1.flags,

fwdbc_4.rev_bc11.r1.flags,
fwdbc_4.rev_bc12.r1.flags,
fwdbc_4.rev_bc13.r1.flags,
fwdbc_4.rev_bc14.r1.flags,
fwdbc_4.rev_bc15.r1.flags,
fwdbc_4.rev_bc16.r1.flags,
fwdbc_4.rev_bc17.r1.flags,
fwdbc_4.rev_bc18.r1.flags,
fwdbc_4.rev_bc19.r1.flags,
fwdbc_4.rev_bc20.r1.flags,

fwdbc_4.rev_bc21.r1.flags,
fwdbc_4.rev_bc22.r1.flags,
fwdbc_4.rev_bc23.r1.flags,
fwdbc_4.rev_bc24.r1.flags,
fwdbc_4.rev_bc25.r1.flags,
fwdbc_4.rev_bc26.r1.flags,
fwdbc_4.rev_bc27.r1.flags,
fwdbc_4.rev_bc28.r1.flags,
fwdbc_4.rev_bc29.r1.flags,
fwdbc_4.rev_bc30.r1.flags,

revbc_1.fwdbc_1.r2f.flags,
revbc_1.fwdbc_2.r2f.flags,
revbc_1.fwdbc_3.r2f.flags,
revbc_1.fwdbc_4.r2f.flags,

revbc_2.fwdbc_1.r2f.flags,
revbc_2.fwdbc_2.r2f.flags,
revbc_2.fwdbc_3.r2f.flags,
revbc_2.fwdbc_4.r2f.flags,

revbc_3.fwdbc_1.r2f.flags,
revbc_3.fwdbc_2.r2f.flags,
revbc_3.fwdbc_3.r2f.flags,
revbc_3.fwdbc_4.r2f.flags,

revbc_4.fwdbc_1.r2f.flags,
revbc_4.fwdbc_2.r2f.flags,
revbc_4.fwdbc_3.r2f.flags,
revbc_4.fwdbc_4.r2f.flags,

revbc_5.fwdbc_1.r2f.flags,
revbc_5.fwdbc_2.r2f.flags,
revbc_5.fwdbc_3.r2f.flags,
revbc_5.fwdbc_4.r2f.flags,

revbc_6.fwdbc_1.r2f.flags,
revbc_6.fwdbc_2.r2f.flags,
revbc_6.fwdbc_3.r2f.flags,
revbc_6.fwdbc_4.r2f.flags,

revbc_7.fwdbc_1.r2f.flags,
revbc_7.fwdbc_2.r2f.flags,
revbc_7.fwdbc_3.r2f.flags,
revbc_7.fwdbc_4.r2f.flags,

revbc_8.fwdbc_1.r2f.flags,
revbc_8.fwdbc_2.r2f.flags,
revbc_8.fwdbc_3.r2f.flags,
revbc_8.fwdbc_4.r2f.flags,

revbc_9.fwdbc_1.r2f.flags,
revbc_9.fwdbc_2.r2f.flags,
revbc_9.fwdbc_3.r2f.flags,
revbc_9.fwdbc_4.r2f.flags,


revbc_10.fwdbc_1.r2f.flags,
revbc_10.fwdbc_2.r2f.flags,
revbc_10.fwdbc_3.r2f.flags,
revbc_10.fwdbc_4.r2f.flags,



revbc_11.fwdbc_1.r2f.flags,
revbc_11.fwdbc_2.r2f.flags,
revbc_11.fwdbc_3.r2f.flags,
revbc_11.fwdbc_4.r2f.flags,

revbc_12.fwdbc_1.r2f.flags,
revbc_12.fwdbc_2.r2f.flags,
revbc_12.fwdbc_3.r2f.flags,
revbc_12.fwdbc_4.r2f.flags,

revbc_13.fwdbc_1.r2f.flags,
revbc_13.fwdbc_2.r2f.flags,
revbc_13.fwdbc_3.r2f.flags,
revbc_13.fwdbc_4.r2f.flags,

revbc_14.fwdbc_1.r2f.flags,
revbc_14.fwdbc_2.r2f.flags,
revbc_14.fwdbc_3.r2f.flags,
revbc_14.fwdbc_4.r2f.flags,

revbc_15.fwdbc_1.r2f.flags,
revbc_15.fwdbc_2.r2f.flags,
revbc_15.fwdbc_3.r2f.flags,
revbc_15.fwdbc_4.r2f.flags,

revbc_16.fwdbc_1.r2f.flags,
revbc_16.fwdbc_2.r2f.flags,
revbc_16.fwdbc_3.r2f.flags,
revbc_16.fwdbc_4.r2f.flags,

revbc_17.fwdbc_1.r2f.flags,
revbc_17.fwdbc_2.r2f.flags,
revbc_17.fwdbc_3.r2f.flags,
revbc_17.fwdbc_4.r2f.flags,

revbc_18.fwdbc_1.r2f.flags,
revbc_18.fwdbc_2.r2f.flags,
revbc_18.fwdbc_3.r2f.flags,
revbc_18.fwdbc_4.r2f.flags,

revbc_19.fwdbc_1.r2f.flags,
revbc_19.fwdbc_2.r2f.flags,
revbc_19.fwdbc_3.r2f.flags,
revbc_19.fwdbc_4.r2f.flags,

revbc_20.fwdbc_1.r2f.flags,
revbc_20.fwdbc_2.r2f.flags,
revbc_20.fwdbc_3.r2f.flags,
revbc_20.fwdbc_4.r2f.flags,

revbc_21.fwdbc_1.r2f.flags,
revbc_21.fwdbc_2.r2f.flags,
revbc_21.fwdbc_3.r2f.flags,
revbc_21.fwdbc_4.r2f.flags,

revbc_22.fwdbc_1.r2f.flags,
revbc_22.fwdbc_2.r2f.flags,
revbc_22.fwdbc_3.r2f.flags,
revbc_22.fwdbc_4.r2f.flags,

revbc_23.fwdbc_1.r2f.flags,
revbc_23.fwdbc_2.r2f.flags,
revbc_23.fwdbc_3.r2f.flags,
revbc_23.fwdbc_4.r2f.flags,

revbc_24.fwdbc_1.r2f.flags,
revbc_24.fwdbc_2.r2f.flags,
revbc_24.fwdbc_3.r2f.flags,
revbc_24.fwdbc_4.r2f.flags,

revbc_25.fwdbc_1.r2f.flags,
revbc_25.fwdbc_2.r2f.flags,
revbc_25.fwdbc_3.r2f.flags,
revbc_25.fwdbc_4.r2f.flags,

revbc_26.fwdbc_1.r2f.flags,
revbc_26.fwdbc_2.r2f.flags,
revbc_26.fwdbc_3.r2f.flags,
revbc_26.fwdbc_4.r2f.flags,

revbc_27.fwdbc_1.r2f.flags,
revbc_27.fwdbc_2.r2f.flags,
revbc_27.fwdbc_3.r2f.flags,
revbc_27.fwdbc_4.r2f.flags,

revbc_28.fwdbc_1.r2f.flags,
revbc_28.fwdbc_2.r2f.flags,
revbc_28.fwdbc_3.r2f.flags,
revbc_28.fwdbc_4.r2f.flags,

revbc_29.fwdbc_1.r2f.flags,
revbc_29.fwdbc_2.r2f.flags,
revbc_29.fwdbc_3.r2f.flags,
revbc_29.fwdbc_4.r2f.flags,

revbc_30.fwdbc_1.r2f.flags,
revbc_30.fwdbc_2.r2f.flags,
revbc_30.fwdbc_3.r2f.flags,
revbc_30.fwdbc_4.r2f.flags,
 
revbc_1.fwdbc_1.r2.flags,
revbc_1.fwdbc_2.r2.flags,
revbc_1.fwdbc_3.r2.flags,
revbc_1.fwdbc_4.r2.flags,

revbc_2.fwdbc_1.r2.flags,
revbc_2.fwdbc_2.r2.flags,
revbc_2.fwdbc_3.r2.flags,
revbc_2.fwdbc_4.r2.flags,

revbc_3.fwdbc_1.r2.flags,
revbc_3.fwdbc_2.r2.flags,
revbc_3.fwdbc_3.r2.flags,
revbc_3.fwdbc_4.r2.flags,

revbc_4.fwdbc_1.r2.flags,
revbc_4.fwdbc_2.r2.flags,
revbc_4.fwdbc_3.r2.flags,
revbc_4.fwdbc_4.r2.flags,

revbc_5.fwdbc_1.r2.flags,
revbc_5.fwdbc_2.r2.flags,
revbc_5.fwdbc_3.r2.flags,
revbc_5.fwdbc_4.r2.flags,

revbc_6.fwdbc_1.r2.flags,
revbc_6.fwdbc_2.r2.flags,
revbc_6.fwdbc_3.r2.flags,
revbc_6.fwdbc_4.r2.flags,

revbc_7.fwdbc_1.r2.flags,
revbc_7.fwdbc_2.r2.flags,
revbc_7.fwdbc_3.r2.flags,
revbc_7.fwdbc_4.r2.flags,

revbc_8.fwdbc_1.r2.flags,
revbc_8.fwdbc_2.r2.flags,
revbc_8.fwdbc_3.r2.flags,
revbc_8.fwdbc_4.r2.flags,

revbc_9.fwdbc_1.r2.flags,
revbc_9.fwdbc_2.r2.flags,
revbc_9.fwdbc_3.r2.flags,
revbc_9.fwdbc_4.r2.flags,

revbc_10.fwdbc_1.r2.flags,
revbc_10.fwdbc_2.r2.flags,
revbc_10.fwdbc_3.r2.flags,
revbc_10.fwdbc_4.r2.flags,

revbc_11.fwdbc_1.r2.flags,
revbc_11.fwdbc_2.r2.flags,
revbc_11.fwdbc_3.r2.flags,
revbc_11.fwdbc_4.r2.flags,

revbc_12.fwdbc_1.r2.flags,
revbc_12.fwdbc_2.r2.flags,
revbc_12.fwdbc_3.r2.flags,
revbc_12.fwdbc_4.r2.flags,

revbc_13.fwdbc_1.r2.flags,
revbc_13.fwdbc_2.r2.flags,
revbc_13.fwdbc_3.r2.flags,
revbc_13.fwdbc_4.r2.flags,

revbc_14.fwdbc_1.r2.flags,
revbc_14.fwdbc_2.r2.flags,
revbc_14.fwdbc_3.r2.flags,
revbc_14.fwdbc_4.r2.flags,

revbc_15.fwdbc_1.r2.flags,
revbc_15.fwdbc_2.r2.flags,
revbc_15.fwdbc_3.r2.flags,
revbc_15.fwdbc_4.r2.flags,


revbc_16.fwdbc_1.r2.flags,
revbc_16.fwdbc_2.r2.flags,
revbc_16.fwdbc_3.r2.flags,
revbc_16.fwdbc_4.r2.flags,

revbc_17.fwdbc_1.r2.flags,
revbc_17.fwdbc_2.r2.flags,
revbc_17.fwdbc_3.r2.flags,
revbc_17.fwdbc_4.r2.flags,

revbc_18.fwdbc_1.r2.flags,
revbc_18.fwdbc_2.r2.flags,
revbc_18.fwdbc_3.r2.flags,
revbc_18.fwdbc_4.r2.flags,

revbc_19.fwdbc_1.r2.flags,
revbc_19.fwdbc_2.r2.flags,
revbc_19.fwdbc_3.r2.flags,
revbc_19.fwdbc_4.r2.flags,

revbc_20.fwdbc_1.r2.flags,
revbc_20.fwdbc_2.r2.flags,
revbc_20.fwdbc_3.r2.flags,
revbc_20.fwdbc_4.r2.flags,


revbc_21.fwdbc_1.r2.flags,
revbc_21.fwdbc_2.r2.flags,
revbc_21.fwdbc_3.r2.flags,
revbc_21.fwdbc_4.r2.flags,

revbc_22.fwdbc_1.r2.flags,
revbc_22.fwdbc_2.r2.flags,
revbc_22.fwdbc_3.r2.flags,
revbc_22.fwdbc_4.r2.flags,

revbc_23.fwdbc_1.r2.flags,
revbc_23.fwdbc_2.r2.flags,
revbc_23.fwdbc_3.r2.flags,
revbc_23.fwdbc_4.r2.flags,

revbc_24.fwdbc_1.r2.flags,
revbc_24.fwdbc_2.r2.flags,
revbc_24.fwdbc_3.r2.flags,
revbc_24.fwdbc_4.r2.flags,

revbc_25.fwdbc_1.r2.flags,
revbc_25.fwdbc_2.r2.flags,
revbc_25.fwdbc_3.r2.flags,
revbc_25.fwdbc_4.r2.flags,

revbc_26.fwdbc_1.r2.flags,
revbc_26.fwdbc_2.r2.flags,
revbc_26.fwdbc_3.r2.flags,
revbc_26.fwdbc_4.r2.flags,
 
revbc_27.fwdbc_1.r2.flags,
revbc_27.fwdbc_2.r2.flags,
revbc_27.fwdbc_3.r2.flags,
revbc_27.fwdbc_4.r2.flags,

revbc_28.fwdbc_1.r2.flags,
revbc_28.fwdbc_2.r2.flags,
revbc_28.fwdbc_3.r2.flags,
revbc_28.fwdbc_4.r2.flags,

revbc_29.fwdbc_1.r2.flags,
revbc_29.fwdbc_2.r2.flags,
revbc_29.fwdbc_3.r2.flags,
revbc_29.fwdbc_4.r2.flags,

revbc_30.fwdbc_1.r2.flags,
revbc_30.fwdbc_2.r2.flags,
revbc_30.fwdbc_3.r2.flags,
revbc_30.fwdbc_4.r2.flags,

fwdbc_1.rev_bc1.r1r.flags,
fwdbc_1.rev_bc2.r1r.flags,
fwdbc_1.rev_bc3.r1r.flags,
fwdbc_1.rev_bc4.r1r.flags,
fwdbc_1.rev_bc5.r1r.flags,
fwdbc_1.rev_bc6.r1r.flags,
fwdbc_1.rev_bc7.r1r.flags,
fwdbc_1.rev_bc8.r1r.flags,
fwdbc_1.rev_bc9.r1r.flags,
fwdbc_1.rev_bc10.r1r.flags,

fwdbc_1.rev_bc11.r1r.flags,
fwdbc_1.rev_bc12.r1r.flags,
fwdbc_1.rev_bc13.r1r.flags,
fwdbc_1.rev_bc14.r1r.flags,
fwdbc_1.rev_bc15.r1r.flags,
fwdbc_1.rev_bc16.r1r.flags,
fwdbc_1.rev_bc17.r1r.flags,
fwdbc_1.rev_bc18.r1r.flags,
fwdbc_1.rev_bc19.r1r.flags,
fwdbc_1.rev_bc20.r1r.flags,

fwdbc_1.rev_bc21.r1r.flags,
fwdbc_1.rev_bc22.r1r.flags,
fwdbc_1.rev_bc23.r1r.flags,
fwdbc_1.rev_bc24.r1r.flags,
fwdbc_1.rev_bc25.r1r.flags,
fwdbc_1.rev_bc26.r1r.flags,
fwdbc_1.rev_bc27.r1r.flags,
fwdbc_1.rev_bc28.r1r.flags,
fwdbc_1.rev_bc29.r1r.flags,
fwdbc_1.rev_bc30.r1r.flags,

fwdbc_2.rev_bc1.r1r.flags,
fwdbc_2.rev_bc2.r1r.flags,
fwdbc_2.rev_bc3.r1r.flags,
fwdbc_2.rev_bc4.r1r.flags,
fwdbc_2.rev_bc5.r1r.flags,
fwdbc_2.rev_bc6.r1r.flags,
fwdbc_2.rev_bc7.r1r.flags,
fwdbc_2.rev_bc8.r1r.flags,
fwdbc_2.rev_bc9.r1r.flags,
fwdbc_2.rev_bc10.r1r.flags,

fwdbc_2.rev_bc11.r1r.flags,
fwdbc_2.rev_bc12.r1r.flags,
fwdbc_2.rev_bc13.r1r.flags,
fwdbc_2.rev_bc14.r1r.flags,
fwdbc_2.rev_bc15.r1r.flags,
fwdbc_2.rev_bc16.r1r.flags,
fwdbc_2.rev_bc17.r1r.flags,
fwdbc_2.rev_bc18.r1r.flags,
fwdbc_2.rev_bc19.r1r.flags,
fwdbc_2.rev_bc20.r1r.flags,

fwdbc_2.rev_bc21.r1r.flags,
fwdbc_2.rev_bc22.r1r.flags,
fwdbc_2.rev_bc23.r1r.flags,
fwdbc_2.rev_bc24.r1r.flags,
fwdbc_2.rev_bc25.r1r.flags,
fwdbc_2.rev_bc26.r1r.flags,
fwdbc_2.rev_bc27.r1r.flags,
fwdbc_2.rev_bc28.r1r.flags,
fwdbc_2.rev_bc29.r1r.flags,
fwdbc_2.rev_bc30.r1r.flags,

fwdbc_3.rev_bc1.r1r.flags,
fwdbc_3.rev_bc2.r1r.flags,
fwdbc_3.rev_bc3.r1r.flags,
fwdbc_3.rev_bc4.r1r.flags,
fwdbc_3.rev_bc5.r1r.flags,
fwdbc_3.rev_bc6.r1r.flags,
fwdbc_3.rev_bc7.r1r.flags,
fwdbc_3.rev_bc8.r1r.flags,
fwdbc_3.rev_bc9.r1r.flags,
fwdbc_3.rev_bc10.r1r.flags,

fwdbc_3.rev_bc11.r1r.flags,
fwdbc_3.rev_bc12.r1r.flags,
fwdbc_3.rev_bc13.r1r.flags,
fwdbc_3.rev_bc14.r1r.flags,
fwdbc_3.rev_bc15.r1r.flags,
fwdbc_3.rev_bc16.r1r.flags,
fwdbc_3.rev_bc17.r1r.flags,
fwdbc_3.rev_bc18.r1r.flags,
fwdbc_3.rev_bc19.r1r.flags,
fwdbc_3.rev_bc20.r1r.flags,

fwdbc_3.rev_bc21.r1r.flags,
fwdbc_3.rev_bc22.r1r.flags,
fwdbc_3.rev_bc23.r1r.flags,
fwdbc_3.rev_bc24.r1r.flags,
fwdbc_3.rev_bc25.r1r.flags,
fwdbc_3.rev_bc26.r1r.flags,
fwdbc_3.rev_bc27.r1r.flags,
fwdbc_3.rev_bc28.r1r.flags,
fwdbc_3.rev_bc29.r1r.flags,
fwdbc_3.rev_bc30.r1r.flags,

fwdbc_4.rev_bc1.r1r.flags,
fwdbc_4.rev_bc2.r1r.flags,
fwdbc_4.rev_bc3.r1r.flags,
fwdbc_4.rev_bc4.r1r.flags,
fwdbc_4.rev_bc5.r1r.flags,
fwdbc_4.rev_bc6.r1r.flags,
fwdbc_4.rev_bc7.r1r.flags,
fwdbc_4.rev_bc8.r1r.flags,
fwdbc_4.rev_bc9.r1r.flags,
fwdbc_4.rev_bc10.r1r.flags,

fwdbc_4.rev_bc11.r1r.flags,
fwdbc_4.rev_bc12.r1r.flags,
fwdbc_4.rev_bc13.r1r.flags,
fwdbc_4.rev_bc14.r1r.flags,
fwdbc_4.rev_bc15.r1r.flags,
fwdbc_4.rev_bc16.r1r.flags,
fwdbc_4.rev_bc17.r1r.flags,
fwdbc_4.rev_bc18.r1r.flags,
fwdbc_4.rev_bc19.r1r.flags,
fwdbc_4.rev_bc20.r1r.flags,

fwdbc_4.rev_bc21.r1r.flags,
fwdbc_4.rev_bc22.r1r.flags,
fwdbc_4.rev_bc23.r1r.flags,
fwdbc_4.rev_bc24.r1r.flags,
fwdbc_4.rev_bc25.r1r.flags,
fwdbc_4.rev_bc26.r1r.flags,
fwdbc_4.rev_bc27.r1r.flags,
fwdbc_4.rev_bc28.r1r.flags,
fwdbc_4.rev_bc29.r1r.flags,
fwdbc_4.rev_bc30.r1r.flags,
"--minimum-length", 10,
"--discard-untrimmed", "--report", "minimal",
"-o",bccut_forward_reads_bac_helianthus[i], "-p",bccut_reverse_reads_bac_helianthus[i],
polycut_forward_reads_bac_helianthus[i],polycut_reverse_reads_bac_helianthus[i]))
}

## **Step 3: Primer Removal**

fwd1<-"GTGCCAGCMGCCGCGGTAA"
fwd2<- "GTGCCAGCMGCWGCGGTAA"
fwd3<- "GTGCCAGCMGCCGCGGTCA"
fwd4<- "GTGKCAGCMGCCGCGGTAA"
rev<- "GGACTACHVGGGTWTCTAAT"


allorientations<-function(primer){       
  require(Biostrings)     
  dna<-DNAString(primer)                                                    
  orientations<-c(Forward=dna, Complement=Biostrings::complement(dna),Reverse=Biostrings::reverse(dna), 
             RevComp=Biostrings::reverseComplement(dna)) 
  return(sapply(orientations,toString))
}

# Next we store all possible orientations of our primers in objects for each primer.
fwd1.ori<-allorientations(fwd1)
fwd2.ori<-allorientations(fwd2)
fwd3.ori<-allorientations(fwd3)
fwd4.ori<-allorientations(fwd4)
rev.ori<-allorientations(rev)


# We then identify occurences of the primers by creating a function called primeroccurences.This function will use the vcountPattern function which will return a vector containing the number of times a particular primer is detected in a sequence and the readFastq function which will take all fastq files in a particular director and turn them into a single object. 
primeroccurences<-function(primer, directory) { 
  nhits<-vcountPattern(primer, sread(readFastq(directory)),fixed=FALSE)
  return(sum(nhits>0))
}

# Create a directory to store the forward and reverse reads after they have been trimmed.
path_primercut_bac_helianthus<-file.path(helianthus_bac_path,"all_files_processed","primer_cutadapt_all_files_processed")
if(!dir.exists(path_primercut_bac_helianthus)) dir.create(path_primercut_bac_helianthus)

primercut_forward_reads_bac_helianthus<-file.path(path_primercut_bac_helianthus,paste0("primercut_",basename(forward_reads_bac_helianthus)))

primercut_reverse_reads_bac_helianthus<-file.path(path_primercut_bac_helianthus,paste0("primercut_",basename(reverse_reads_bac_helianthus)))

use_condaenv(condaenv="/Users/aarononfurak/anaconda3/envs/cutadaptenv/bin/python")
system2("conda",args=c("run","-n","cutadaptenv","cutadapt --version"),stdout="")

# We then create objects containing the forward and reverse primer reverse compliment strings. By using the :: syntax we are able to call a function stored in the dada2 package without having to load the whole dada2 package. In this case we will call the rc function of the dada2 package. The rc function takes a sequence object provided by the user and creates the reverse compliment of the sequence. 
fwd.rc1<-dada2:::rc(fwd1)
fwd.rc2<-dada2:::rc(fwd2)
fwd.rc3<-dada2:::rc(fwd3)
fwd.rc4<-dada2:::rc(fwd4) 
rev.rc<-dada2:::rc(rev)

# Using the paste function we then create objects that contain the flags for the potential combinations of each forward and reverse primer and the reverse compliment. These flags will serve as the argumentst that we provide to cutadapt. The ^ at the beginning of the sequence indicates that the primer should be removed from the beginning of the sequence. 
fwd1.r1.flags<-paste("-a"," ", "^", fwd1,"...",rev.rc, sep='') 
fwd2.r1.flags<-paste("-a"," ", "^", fwd2,"...",rev.rc, sep='') 
fwd3.r1.flags<-paste("-a"," ", "^", fwd3,"...",rev.rc, sep='')
fwd4.r1.flags<-paste("-a"," ", "^", fwd4,"...",rev.rc, sep='') 

r1.fwd1.flags<-paste("-a"," ", "^", rev,"...",fwd.rc1, sep='')
r1.fwd2.flags<-paste("-a"," ", "^", rev,"...",fwd.rc2, sep='')
r1.fwd3.flags<-paste("-a"," ", "^", rev,"...",fwd.rc3, sep='')
r1.fwd4.flags<-paste("-a"," ", "^", rev,"...",fwd.rc4, sep='')


rev.fwd1.flags<-paste("-A"," ", "^", rev,"...",fwd.rc1, sep='')
rev.fwd2.flags<-paste("-A"," ", "^", rev,"...",fwd.rc2, sep='')
rev.fwd3.flags<-paste("-A"," ", "^", rev,"...",fwd.rc3, sep='')
rev.fwd4.flags<-paste("-A"," ", "^", rev,"...",fwd.rc4, sep='')

fwd1.rev.flags<-paste("-A"," ", "^", fwd1,"...",rev.rc, sep='')
fwd2.rev.flags<-paste("-A"," ", "^", fwd2,"...",rev.rc, sep='')
fwd3.rev.flags<-paste("-A"," ", "^", fwd3,"...",rev.rc, sep='')
fwd4.rev.flags<-paste("-A"," ", "^", fwd4,"...",rev.rc, sep='')

# We then use cutadapt to remove the primers from each read. Because we have twelve pairs of forward and reverse primers we instruct cutadapt to make 12 passes through the forward reads and twelve passes through the reverse reads for each possible primer pair using the -n 12 flag.

for (i in seq_along(forward_reads_bac_helianthus)){
  system2("conda",args=c("run","-n","cutadaptenv","cutadapt",fwd1.r1.flags,
                          fwd2.r1.flags,
                          fwd3.r1.flags,
                          fwd4.r1.flags,
                          r1.fwd1.flags,
                          r1.fwd2.flags,
                          r1.fwd3.flags,
                          r1.fwd4.flags,
                          rev.fwd1.flags,
                          rev.fwd2.flags,
                          rev.fwd3.flags,
                          rev.fwd4.flags,
                          fwd1.rev.flags,
                          fwd2.rev.flags,
                          fwd3.rev.flags,
                          fwd4.rev.flags,
                          "--discard-untrimmed", "--minimum-length",10,"--report","minimal",
                          "-o",primercut_forward_reads_bac_helianthus[i], "-p",primercut_reverse_reads_bac_helianthus[i],
                         bccut_forward_reads_bac_helianthus[i],bccut_reverse_reads_bac_helianthus[i]))
}

# Next we create two path objects that we will store the paths for our filtered forward and reverse reads. 
filtered_forward_reads_bac_helianthus_01<-file.path(helianthus_bac_path,"all_files_processed","filtered_all_files_processed",paste0("filtered_",basename(forward_reads_bac_helianthus)))
filtered_reverse_reads_bac_helianthus_01<-file.path(helianthus_bac_path,"all_files_processed","filtered_all_files_processed",paste0("filtered_",basename(reverse_reads_bac_helianthus)))


# We then filter our forward and reverse reads using the filterAndTrim function. 
filterAndTrim(primercut_forward_reads_bac_helianthus,filtered_forward_reads_bac_helianthus_01,primercut_reverse_reads_bac_helianthus,filtered_reverse_reads_bac_helianthus_01,maxEE=c(2,2),multithread = FALSE,rm.phix = TRUE)

filtered_forward_reads_bac_helianthus<-filtered_forward_reads_bac_helianthus_01[grep("filtered_Negative_b.raw_1",filtered_forward_reads_bac_helianthus_01,invert = TRUE)]
filtered_reverse_reads_bac_helianthus<-filtered_reverse_reads_bac_helianthus_01[grep("filtered_Negative_b.raw_2",filtered_reverse_reads_bac_helianthus_01,invert=TRUE)]


quality_plot_primer_cut_filter_fwd<-plotQualityProfile(filtered_forward_reads_bac_helianthus,aggregate=TRUE)
quality_plot_primer_cut_filter_fwd
quality_plot_primer_cut_filter_rev<-plotQualityProfile(filtered_reverse_reads_bac_helianthus,aggregate=TRUE)
quality_plot_primer_cut_filter_rev

# dereplication(merging identical reads into single sequences)
derepforward_bac_helianthus<-derepFastq(filtered_forward_reads_bac_helianthus,verbose=TRUE,n = 1e4)
derepreverse_bac_helianthus<-derepFastq(filtered_reverse_reads_bac_helianthus,verbose=TRUE,n = 1e4)
```

# This section of the analyses was run on a server due to its high memory requirements.
```{r}
# Next we create two path objects that we will store the paths for our filtered forward and reverse reads. 
filtered_forward_reads_its_helianthus<-list.files("/sphinx_local/projects/michelle/helianthus/cultureindependent_data/raw_data/fungi/05_2024_sequence_processing/05_2024_trimmed_v4_files",pattern="r1.fq.gz|.raw_1.fq.gz",full.names = TRUE)
filtered_reverse_reads_its_helianthus<-list.files("/sphinx_local/projects/michelle/helianthus/cultureindependent_data/raw_data/fungi/05_2024_sequence_processing/05_2024_trimmed_v4_files",pattern="r2.fq.gz|.raw_2.fq.gz",full.names = T)
length(filtered_forward_reads_its_helianthus)
length(filtered_reverse_reads_its_helianthus)

# Learning errors for forward and reverse reads

error_forward_reads_its_helianthus<-learnErrors(filtered_forward_reads_its_helianthus,multithread = 20)
error_reverse_reads_its_helianthus<-learnErrors(filtered_reverse_reads_its_helianthus,multithread=20)

plotErrors(error_forward_reads_its_helianthus,nominalQ = TRUE)
plotErrors(error_reverse_reads_its_helianthus,nominalQ = TRUE)

dada_forward_reads_its_helianthus<-dada(filtered_forward_reads_its_helianthus,err=error_forward_reads_its_helianthus,pool="pseudo",multithread = 20)

dada_reverse_reads_its_helianthus<-dada(filtered_reverse_reads_its_helianthus,err=error_reverse_reads_its_helianthus,pool="pseudo",multithread = 20)

# First forward and reverse reads are merged using mergePairs. 
merge_its_helianthus<-mergePairs(dada_forward_reads_its_helianthus,filtered_forward_reads_its_helianthus,dada_reverse_reads_its_helianthus,filtered_reverse_reads_its_helianthus,verbose=TRUE,maxMismatch = 0)


# We then create a sequence table
seqtab_its_helianthus<-makeSequenceTable(merge_its_helianthus)


# Inspect distribution of sequence lengths
table(nchar(getSequences(seqtab_its_helianthus)))

# We then remove chimeras using the removeBimeraDenovo function. WRITE TABLE
seqtab_nochim_its_helianthus<-removeBimeraDenovo(seqtab_its_helianthus,method="consensus", multithread=TRUE, verbose=TRUE)
write.csv(seqtab_nochim_its_helianthus, "seqtab_nochim_16_helianthus.csv", row.names=TRUE)
```

    